---
title: "covid 19"
author: "Jennifer Nava"
date: "07/25/21"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits=2)
require(tidyverse)
require(tigerstats)
require(lubridate)
kRdata <- read.csv(file = 'kRdata.csv')
```
### Data is from the Patient_Info dataset from South Korea 1 Jan to 1 May 
### This is contained in a downloadable zip file from kaggle

Some of the data was uncoded for sex - sex must be just male or female
77 of the data entries were coded sex  as blank, so we omit these.
state of a patient must be died or alive - we adjust that as well   
  
# Question 1 - Is dying independent of sex




Table of patients:
```{r}

# cross tabulation, patient state by gender

with(kRdata, table(Sex, result))

```

No, dying is a dependent variable of sex. Dying is the outcome of people who got covid 19.


## We create two bar charts - one based on frequency and the other on percent, use ggplot commands to do this



#### Plot barplots ggplot way

```{r}
dd2 <- kRdata %>% group_by(result,sex) %>% summarize(count=n()) %>% mutate(prcnt=count/sum(count))


# the group_by followed by summarize(count=n())

basicC <- ggplot(dd2,aes(x=result,y=count,fill=sex))
basicC + geom_bar(stat="identity",position="dodge")

#Now for percentage plot

basicCC <- ggplot(dd2,aes(x=result,y=prcnt*100,fill=sex)) 
basicCC + geom_bar(stat="identity", position = "dodge")
```


#### Plot barplots tigerstats way

```{r}
barchartGC(~result + sex,data=kRdata)
barchartGC(~result + sex,data=kRdata, type="percent")

```

  
These results tell me that women are more likely to get infected with covid 19 and live, and it also tells me that there has been more death cases in men than women once they are infected with covid 19. These graphs also show me that there has been more than 20% more deaths in men once they are infected with covid 19, and there has been more than 10% of cases in women than men who have lived once they got infected with covid 19. 


  
## Numerical results

```{r}
table1 <- xtabs(~result + sex, data=kRdata)
rowPerc(table1)
colPerc(table1)
```

These numerical results tell me that for every 100 people who got infected with covid 19 56 were female and 44 were male who lived. It also tells me that out of every 100 people who got infected with covid 19 36 were women who died and 64 were men and died. The second numerical results tell me that 98.7% of women lived after contracting covid 19 and 1.4% of those women died after getting covid 19. It also tells me that 97% of men lived after contracting covid 19 and 3% died. 

## Inferential results 




## Conclusions

